### 2018-04-10 Writing/CoverLetter.tex
Rewrote the cover letter

Despite being at the base of almost every endeavour in modern Biology, the assumption made in tree inference that phylogenetic data is independent is probably mostly erroneous.
In fact, since the advent of Cladistics in the 1950s, evolutionary biologists have made the assumption that characters used to build a phylogeny are independent despite the fact that we are looking at their variance-covariance to build phylogenetic hypothesis.
This effect is somewhat negligible in molecular phylogenetics because the huge amount of available data is thought to temper down the correlation effect.
However, in smaller morphological datasets, this can lead to pretty big biases and can easily favour on topology from another simply with a ``judicious'' choice of characters.

Our research article, entitled ``Influence of different modes of morphological character correlation on tree inference'', is - to our knowledge - the first to thoroughly test the effect of character correlation on tree topology using a thorough simulation framework ($>$ 100 CPU years worth).
Using a novel metric to measure the amount of phylogenetic correlation in a matrix, we tested different scenario that either increase or decrease the amount of correlation of characters generated from a known ``true'' tree and compare how these levels of correlation affect our ability to recover this topology using both Maximum Parsimony and Bayesian inference.

Our results suggests that strong levels of correlation can negatively impact our ability to recover the correct tree topology and more so in Maximum Parsimony than in Baysian.
However, it is encouraging to see that low levels of correlation do not especially impact the topology, at least not to the extant where researchers should specifically collect only uncorrelated characters.
Finally, we show that, for smaller datasets, Maximum Parsimony and Bayesian inference are both pretty efficient to recover the correct topology, regardless of the amount of correlation

>>>>

Despite being at the base of almost every endeavour in modern Biology, the assumption made in tree inference that phylogenetic data is independent is probably mostly erroneous.
This assumption was stated since the advent of Cladistics in the 1950s but is nowadays mainly ignored in phylogenetic endeavour.
In fact, this effect can be neglected in molecular datasets because the huge amount of available data is thought to temper down the correlation effect.
However, in morphological datasets, where the amount of characters is much smaller, character correlation can lead to significant biases especially by favouring one topology from another due to a specific choice of characters (whether this is done consciously by researchers or not).
With the ``resurgence'' of morphological data phylogenetic analysis (namely with the Total Evidence tip-dating method, Ronquist \textit{et al.}, 2012, Sys. Biol), it is thus important to acknowledge limitations and caveats that come with the use of such data, namely how correlation patterns in morphological datasets can effect tree inference.

In our research article, entitled ``Influence of different modes of morphological character correlation on tree inference'', we propose the first - to our knowledge - simulation based test of the effect of character correlation on tree topology using a thorough simulation framework ($>$ 100 CPU years worth).
Using a novel metric to measure direct phylogenetic correlation between characters, we simulated discrete morphological datasets that we then modified to increase or decrease character correlation.
We then measured the resulting topological differences (from both maximum parsimony and Bayesian trees) to measure the effect of character correlation in the light of our known simulated parameters.

Our results suggest that datasets that have higher levels of internal correlation negatively impact our ability to recover the correct tree topology.
This is too be contrasted with datasets that have low levels of correlation (i.e. more noisy) which can still recover the correct topology, depending on the amount of data and the inference method used.
These results, although non-surprising to researchers in the field, are the first - to our knowledge - to actually quantify the effect of character correlation and provides practical data and reusable code allowing researcher to effectively measure the limitations of their datasets.
Furthermore, we suggest that using our proposed new metric, it would be able to ``bias'' bootstrap pseudo-replications in phylogenetic analysis by favouring character with high or low correlation, depending on the purpose of the phylogenetic search.
